Estimating duration using survival analysis

### 2024-07-29 cis-perfect-testing.tex
Rob p97 comment

I first approximate the \cref{E-ATACCC} posterior estimate of the hazard as $\logit{\vec{h}} \dist \MNorm(\vec{\mu}_A, \matr{\Sigma}_A)$ where $\vec{h}$ is the hazard, and $\vec{\mu}_A$ and $\matr{\Sigma}_A$ are the mean and covariance matrix computed from the samples of $\logit{\vec{h}}$ derived using the method of \cref{ATACCC:sec:duration}.
Using a multivariate normal, as opposed to multiple univariate distribution for each $h_t$, preserves the correlation between the hazards.
% The logit transformation maps from the $[0, 1]$ interval to the full real line.
The approximation is very good (see \cref{perf-test:fig:approximate-ATACCC-hazard} and \cref{perf-test:fig:approximate-ATACCC-survival}).
\begin{figure}
  \thisfloatpagestyle{empty}
  % \vspace{-1cm}
  \makebox[\textwidth][c]{\includegraphics[width=.9\paperwidth]{cis-perfect-testing/ataccc-approximation-hazard}}
  \caption[Approximating the ATACCC posterior hazard as a logit-normal]{Comparison of the posterior estimate of the hazard from \cref{E-ATACCC} and its approximation with a logit-normal distribution (kernel density estimate smoothed) for hazards between day 4 and 15. The density for smaller hazards is concentrated very close to 0. \label{perf-test:fig:approximate-ATACCC-hazard}}
\end{figure}
\begin{figure}
  \centering \includegraphics{cis-perfect-testing/ataccc-approximation-survival}
  \caption[Approximating the ATACCC posterior survival]{Comparison of the posterior estimate of the survival from \cref{E-ATACCC} and its approximation with a logit-normal distribution (median and central 95\% interval). The survival is a function of all the hazards up until that point, therefore the correlation between the hazards must be well-approximated to have these agree. \label{perf-test:fig:approximate-ATACCC-survival}}
\end{figure}

>>>>

I first approximate the \cref{E-ATACCC} posterior estimate of the hazard as $\logit{\vec{h}} \dist \MNorm(\vec{\mu}_A, \matr{\Sigma}_A)$ where $\vec{h} = [h_1, \dots, h_{\dmax}]^T$ is the hazard, and $\vec{\mu}_A$ and $\matr{\Sigma}_A$ are the mean and covariance matrix computed from the samples of $\logit{\vec{h}}$ derived using the method of \cref{E-ATACCC:sec:duration}.
Therefore, $\vec{h}$ represents a sample from the approximation of \cref{E-ATACCC}'s posterior estimate of the hazard before increasing the uncertainty to account for the strong model assumptions.
Using a multivariate normal, as opposed to multiple univariate distribution for each $h_t$, preserves the correlation between the hazards.
% The logit transformation maps from the $[0, 1]$ interval to the full real line.
The approximation is very good (see \cref{perf-test:fig:approximate-ATACCC-hazard} and \cref{perf-test:fig:approximate-ATACCC-survival}).
\begin{figure}
  \thisfloatpagestyle{empty}
  % \vspace{-1cm}
  \makebox[\textwidth][c]{\includegraphics[width=.9\paperwidth]{cis-perfect-testing/ataccc-approximation-hazard}}
  \caption[Approximating the ATACCC posterior hazard as a logit-normal]{Comparison of the posterior estimate of the hazard from \cref{E-ATACCC} and its approximation with a logit-normal distribution (kernel density estimate smoothed) for hazards between day 4 and 15. The density for smaller hazards is concentrated very close to 0. \label{perf-test:fig:approximate-ATACCC-hazard}}
\end{figure}
\begin{figure}
  \centering \includegraphics{cis-perfect-testing/ataccc-approximation-survival}
  \caption[Approximating the ATACCC posterior survival]{Comparison of the posterior estimate of the survival from \cref{E-ATACCC} and its approximation with a logit-normal distribution (median and central 95\% interval). The survival is a function of all the hazards up until that point, therefore the correlation between the hazards must be well-approximated to have these agree. \label{perf-test:fig:approximate-ATACCC-survival}}
\end{figure}
